Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-11-05 RR_manuscript/Draft_RR.tex
fix model_desc medians (see line 1046(old) or 1053(new))

At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 4 models per team.
Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.

@@

\caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis. The data set included analyses from 30 teams and  109 analysts.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrr}
\toprule
\bf{Team characteristics} &    & \bf{Range} & \bf{Median}\\
\midrule
 & Team size & 1.0 -- 12.0 & 3.0\\
 & Years after PhD & -3.8 -- 12.4 & 5.8\\
 & Prior belief & 48.5 -- 92.0 & 70.0\\
 & Acoustic analysis peer rating & 41.2 -- 88.3 & 75.2\\
 & Statistical analysis peer rating & 33.0 -- 93.3 & 74.1\\
 & Overall peer rating & 39.0 -- 88.7 & 72.2\\
 &  &  \vphantom{5} & \\
\bf{Acoustic analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Outcome & F0 & 37 & 36\\
 & Duration & 36 & 35\\
 & Intensity & 15 & 14\\
 & Formants & 13 & 12\\
 & Other & 3 & 3\\
 &  &  \vphantom{4} & \\
\hspace{1em}Temporal window & Segment & 47 & 46\\
 & Word & 45 & 44\\
 & Sentence & 4 & 4\\
 & Phrase & 3 & 3\\
 & Other & 4 & 4\\
 &  &  \vphantom{3} & \\
\hspace{1em}Typicality operationalization & Categorical & 75 & 73\\
 & Continuous (mean) & 25 & 24\\
 & Continuous (median) & 3 & 3\\
 &  &  \vphantom{2} & \\
\bf{Statistical analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Framework & Frequentist & 86 & 83\\
 & Bayesian & 18 & 17\\
 &  &  \vphantom{1} & \\
\hspace{1em}Model & Linear model & 102 & 98\\
 & GAM & 1 & 1\\
 & Other & 1 & 1\\
 &  &  & \\
 &  & \bf{Range} & \bf{Median}\\
\hspace{1em}N & Models & 1 -- 16 & 4\\
 & Predictors & 1 -- 5 & 2\\
 & Random terms & 1 -- 10 & 2\\
\hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}2\\
\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}1\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 3 models per team.
Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.

@@

\caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis. The data set included analyses from 30 teams and  109 analysts.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrr}
\toprule
\bf{Team characteristics} &    & \bf{Range} & \bf{Median}\\
\midrule
 & Team size & 1.0 -- 12.0 & 3.0\\
 & Years after PhD & -3.8 -- 12.4 & 5.8\\
 & Prior belief & 48.5 -- 92.0 & 70.0\\
 & Acoustic analysis peer rating & 41.2 -- 88.3 & 75.2\\
 & Statistical analysis peer rating & 33.0 -- 93.3 & 74.1\\
 & Overall peer rating & 39.0 -- 88.7 & 72.2\\
 &  &  \vphantom{5} & \\
\bf{Acoustic analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Outcome & F0 & 37 & 36\\
 & Duration & 36 & 35\\
 & Intensity & 15 & 14\\
 & Formants & 13 & 12\\
 & Other & 3 & 3\\
 &  &  \vphantom{4} & \\
\hspace{1em}Temporal window & Segment & 47 & 46\\
 & Word & 45 & 44\\
 & Sentence & 4 & 4\\
 & Phrase & 3 & 3\\
 & Other & 4 & 4\\
 &  &  \vphantom{3} & \\
\hspace{1em}Typicality operationalization & Categorical & 75 & 73\\
 & Continuous (mean) & 25 & 24\\
 & Continuous (median) & 3 & 3\\
 &  &  \vphantom{2} & \\
\bf{Statistical analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Framework & Frequentist & 86 & 83\\
 & Bayesian & 18 & 17\\
 &  &  \vphantom{1} & \\
\hspace{1em}Model & Linear model & 102 & 98\\
 & GAM & 1 & 1\\
 & Other & 1 & 1\\
 &  &  & \\
 &  & \bf{Range} & \bf{Median}\\
\hspace{1em}N & Models & 1 -- 16 & 3\\
 & Predictors & 1 -- 5 & 2\\
 & Random terms & 1 -- 10 & 2\\
\hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}2\\
\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}0\\
\bottomrule
\end{tabular}}
\end{table}
